# Screening Thresholds #
```{r}
reg <- function(m,x,b){
      y <- m * x + b
      return(round(y, digits = 3))
}

cutoff <- 49.9 ## cutoff
failsafe <- 117.5 ## threshold
```
* IRT screening employs two rolling percentile thresholds
    * 96%tile from a 4 week period ~ 49.9 ng/ml
    * 99%tile from a 12 week period ~ 117.5 ng/ml

* Comparison data from samples near the screening thresholds was used to calculate regression equation


## 96th percentile ##
* The comparison data set was filtered to remove values less than 30 ng/ml and greater than 70.

```{r, fig.cap="\\label{fig:dem}Filtered Deming regression"}
co <- comp %>% ## comp is created in the comparison file
     filter(AD >= 30 & AD <= 70)  ## data close to the 96%tile

co.deming <- mcreg(x = co$AD, y =co$GSP, error.ratio = 1, alpha = 0.05,
                     mref.name = "AD", mtest.name = "GSP", sample.names = NULL,
                     method.reg = "Deming", method.ci = "bootstrap",
                     method.bootstrap.ci = "BCa",
                     nsamples = 999, rng.seed = NULL, rng.kind = "Mersenne-Twister", iter.max = 30,
                     threshold = 1e-06, na.rm = TRUE, NBins = 1e+06)

plot(co.deming, x.lab = "AD", y.lab = "GSP", main=paste(params$analyte, "Filtered Method Comparision"))
```

```{r}    
pander::pander(co.deming@para, caption = "\\label{tab:co}Regression Parameters")
```

```{r,fig.cap="\\label{fig:diff}Difference Plot"}
plotDifference(co.deming, main= paste(params$analyte, "Method Comparision"))
```

```{r}
cointercept <- co.deming@para[1,1] # intercept
coslope <- co.deming@para[2,1] # slope
``` 
  
* The regression parameters (table \ref{tab:co}) were used to
  determine the effect of the GSP method  on the 96%tile  screening threshold.

* A `r params$analyte` result of `r reg(coslope, cutoff, cointercept)`
  `r info$units` on the GSP platform is equivalent to a value at the
  screening threshold (`r cutoff` `r info$units`) with the AutoDelfia.
  
## 99th percentile ##

* The comparison data set was filtered to remove values less than 60 ng/ml and greater than `r info$upper`.

```{r, fig.cap="\\label{fig:dem}Filtered Deming regression"}
fs <- comp %>%
     filter(AD >= 50 & AD <= info$upper) 

fs.deming <- mcreg(x = fs$AD, y =fs$GSP, error.ratio = 1, alpha = 0.05,
                     mref.name = "AD", mtest.name = "GSP", sample.names = NULL,
                     method.reg = "Deming", method.ci = "bootstrap",
                     method.bootstrap.ci = "BCa",
                     nsamples = 999, rng.seed = NULL, rng.kind = "Mersenne-Twister", iter.max = 30,
                     threshold = 1e-06, na.rm = TRUE, NBins = 1e+06)

plot(fs.deming, x.lab = "AD", y.lab = "GSP", main=paste(params$analyte, "Filtered Method Comparision"))
```

```{r}    
pander::pander(fs.deming@para, caption = "\\label{tab:fs}Regression Parameters")
```

```{r,fig.cap="\\label{fig:diff}Difference Plot"}
plotDifference(fs.deming, main= paste(params$analyte, "Method Comparision"))
```

```{r}
fsintercept <- fs.deming@para[1,1] # intercept
fsslope <- fs.deming@para[2,1] # slope
``` 

* The regression parameters (table \ref{tab:fs}) were used to
  determine the effect of the GSP method  on the 99%tile  fail-safe threshold.

* A `r params$analyte` result of `r reg(fsslope, failsafe,
  fsintercept)` `r info$units` on the GSP platform is equivalent to a
  value at the screening threshold (`r failsafe` `r info$units`)
  with the AutoDelfia.

\FloatBarrier

