---
title: "GSP Method Verification"
author: Sven Eberhard, Amy Chambers and Matthew Henderson
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
    pdf_document:
        keep_tex: false
        includes:
            in_header: ../resources/header.tex
        fig_caption: yes
        number_sections: yes
fontsize: 11pt 
geometry: margin=1in
params:
    analyte: 
        label: "Analyte:"
        value: "TSH"
        input: select
        choices: [TSH, N17P, IRT]
    file: 
        label: "Input dataset:"
        value: ./data/N17P_GSP_validation.xls
        input: text
---

\begin{center}
\includegraphics[width = 60mm]{../resources/NSO_logo.pdf}
\end{center}

\tableofcontents 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=TRUE, warning=FALSE, fig.height=4, fig.width=6)
```

```{r}
library("dplyr")
library("magrittr")
library("ggplot2")
library("tidyr")
library("mcr")
library("readxl")
library("pander")
library("qcc")

## Used for testing
## params <- list(analyte = "N17P", file = "../data/N17P_GSP_validation.xls")
## params <- list(analyte = "IRT", file = "../data/IRT_GSP_validation.xls")
## params <- list(analyte = "TSH", file = "../data/TSH_GSP_validation.xls")
                 
## set analyte_info dependant on analyte
 info <- switch(params$analyte,
                "TSH" = list(units = "mIU/L", threshold_doc = "TSH_threshold.Rmd",
                             lower = 1.31, upper = 250),
                "N17P" = list(units = "nmol/L", threshold_doc = "N17P_threshold.Rmd",
                              lower = 0, upper = 299.2),
                "IRT" = list(units = "ng/ml", threshold_doc = "IRT_threshold.Rmd",
                             lower = 9, upper = 500))

## excel workbook sheets
sheets <- list(comp = 1, precision = 2, prelim = 3, linearity = 8, lob = 5, inter = 9)

## getwd()
## N17OHP ng/mL -> nmol/L conversion factor 1.36
## N17OHP 1.4ng/mL to 220ng/mL
## N17OHP 1.904 nmol/L to 299.2 nmol/L
## NTSH 1.31uU/mL to 250uU/mL
## IRT 9ng/ml to 500ng/mL
```
# Background

# Methods

# Recommendations

## Sample type

## Sample stability

## Analytical Measurement Range

Analytical measurement range (AMR) is determined by the manufacturer for each kit lot. The AMR for the kit lot used in this validation is 


```{r child = 'precsion.Rmd'}
```
\newpage
```{r child = 'amr.Rmd'}
```
\newpage
```{r child = 'comparison.Rmd'}
```
\newpage
```{r child = info$threshold_doc}
```
\newpage
```{r child = 'inter.Rmd'}
```
\newpage
```{r child = 'interference.Rmd'}
```
