# Screening Thresholds #

```{r}
reg <- function(m,x,b){
      y <- m * x + b
      return(round(y, digits = 3))
}

conc1 <- 38
conc3 <- 55
conc4 <- 105
conc5 <- 200
conc6 <- 52
conc7 <- 91
conc8 <- 160
alert1 <- 120
alert2 <- 200
alert3 <- 300
```

* CAH screening employs GA and BW specific screening thresholds:
    * GA: 38, 55, 105, 200
    * BW: 38, 52, 91, 160
    * Alert: 120, 200, 300

* Comparison data from samples near the screening thresholds was used to calculate regression equations

## Conservative Threshold: "conc1, "conc2" and "conc9" ##

* Threshold used when:
    * GA $\ge$ 36.1 ww.d 
    * BW $\ge$ 2500 g 
    * AOC $\ge$ 420 hours
    * BW and GA are unknown

* The comparison data set was filtered to remove values <20 nmol/L and >60 nmol/L.

```{r, fig.cap="\\label{fig:dem}Filtered Deming regression"}
conservative <- comp %>%  ## comp is created in the comparison file
     filter(AD >= 20 & AD <= 60)  ## data close to the borderline threshold

conservative.deming <- mcreg(x = conservative$AD, y =conservative$GSP, error.ratio = 1, alpha = 0.05,
                     mref.name = "AD", mtest.name = "GSP", sample.names = NULL,
                     method.reg = "Deming", method.ci = "bootstrap",
                     method.bootstrap.ci = "BCa",
                     nsamples = 999, rng.seed = NULL, rng.kind = "Mersenne-Twister", iter.max = 30,
                     threshold = 1e-06, na.rm = TRUE, NBins = 1e+06)

plot(conservative.deming, x.lab = "AD", y.lab = "GSP", main=paste(params$analyte, "Conservative Threshold Comparison"))
```

```{r}    
pander::pander(conservative.deming@para, caption = "\\label{tab:conservative}Regression Parameters")
```

```{r,fig.cap="\\label{fig:diff}Difference Plot"}
plotDifference(conservative.deming, main= paste(params$analyte, "Threshold Comparision"))
```

```{r}
conservativeintercept <- conservative.deming@para[1,1] # intercept
conservativeslope <- conservative.deming@para[2,1] # slope
``` 
  
* The regression parameters (table \ref{tab:conservative}) were used to
  determine the effect of the GSP method on the conservative threshold.

* A `r params$analyte` result of `r reg(conservativeslope, conc1,
  conservativeintercept)` `r info$units` on the GSP platform is
  equivalent to the conservative threshold (`r conc1` `r info$units`) with the
  AutoDelfia.

\FloatBarrier
  
## Transfer of "conc3" and "conc6" thresholds

* "conc3" GA 35.1 - 36.0 = 55 
* "conc6" GW 1500 - 2400 = 52

* The comparison data set was filtered to remove values <32 nmol/L and >75 nmol/L.

```{r, fig.cap="\\label{fig:dem36}Filtered Deming regression"}
conc36 <- comp %>%  ## comp is created in the comparison file
     filter(AD >= 32 & AD <= 75)  ## data close to the threshold

conc36.deming <- mcreg(x = conc36$AD, y =conc36$GSP, error.ratio = 1, alpha = 0.05,
                     mref.name = "AD", mtest.name = "GSP", sample.names = NULL,
                     method.reg = "Deming", method.ci = "bootstrap",
                     method.bootstrap.ci = "BCa",
                     nsamples = 999, rng.seed = NULL, rng.kind = "Mersenne-Twister", iter.max = 30,
                     threshold = 1e-06, na.rm = TRUE, NBins = 1e+06)

plot(conc36.deming, x.lab = "AD", y.lab = "GSP", main=paste(params$analyte, "Conc3 and Conc6 Thresholds Comparison"))
```

```{r}    
pander::pander(conc36.deming@para, caption = "\\label{tab:conc36}Regression Parameters")
```

```{r,fig.cap="\\label{fig:diff36}Difference Plot"}
plotDifference(conc36.deming, main= paste(params$analyte, "Threshold Comparision"))
```

```{r}
conc36intercept <- conc36.deming@para[1,1] # intercept
conc36slope <- conc36.deming@para[2,1] # slope
``` 
  
* The regression parameters (table \ref{tab:conc36}) were used to
  determine the effect of the GSP method on the Conc3 and Conc6 thresholds.

* A `r params$analyte` result of `r reg(conc36slope, conc3,
  conc36intercept)` `r info$units` on the GSP platform is
  equivalent to "conc3" threshold (`r conc3` `r info$units`) with the
  AutoDelfia.
  
  
* A `r params$analyte` result of `r reg(conc36slope, conc6,
  conc36intercept)` `r info$units` on the GSP platform is
  equivalent to "conc6" threshold (`r conc6` `r info$units`) with the
  AutoDelfia.
  
  
\FloatBarrier

## Transfer of "conc4" and "conc7" and "alert1"

* "conc4" GA 33.1-35.0 = 105
* "conc7" GW 1000-1499 = 91
* Conservative "alert1" = 120

* The comparison data set was filtered to remove values <70 nmol/L and >140 nmol/L.

```{r, fig.cap="\\label{fig:dem47}Filtered Deming regression"}
conc47 <- comp %>%  ## comp is created in the comparison file
     filter(AD >= 70 & AD <= 140)  ## data close to the threshold

conc47.deming <- mcreg(x = conc47$AD, y =conc47$GSP, error.ratio = 1, alpha = 0.05,
                     mref.name = "AD", mtest.name = "GSP", sample.names = NULL,
                     method.reg = "Deming", method.ci = "bootstrap",
                     method.bootstrap.ci = "BCa",
                     nsamples = 999, rng.seed = NULL, rng.kind = "Mersenne-Twister", iter.max = 30,
                     threshold = 1e-06, na.rm = TRUE, NBins = 1e+06)

plot(conc47.deming, x.lab = "AD", y.lab = "GSP", main=paste(params$analyte, "Conc4 and Conc7 Thresholds Comparison"))
```

```{r}    
pander::pander(conc47.deming@para, caption = "\\label{tab:conc47}Regression Parameters")
```

```{r,fig.cap="\\label{fig:diff47}Difference Plot"}
plotDifference(conc47.deming, main= paste(params$analyte, "Threshold Comparision"))
```

```{r}
conc47intercept <- conc47.deming@para[1,1] # intercept
conc47slope <- conc47.deming@para[2,1] # slope
``` 
  
* The regression parameters (table \ref{tab:conc47}) were used to
  determine the effect of the GSP method on the Conc3 and Conc6 thresholds.

* A `r params$analyte` result of `r reg(conc47slope, conc4,
  conc47intercept)` `r info$units` on the GSP platform is
  equivalent to "conc4" threshold (`r conc4` `r info$units`) with the
  AutoDelfia.
  
* A `r params$analyte` result of `r reg(conc47slope, conc7,
  conc47intercept)` `r info$units` on the GSP platform is
  equivalent to "conc7" threshold (`r conc7` `r info$units`) with the
  AutoDelfia.

* A `r params$analyte` result of `r reg(conc47slope, alert1,
  conc47intercept)` `r info$units` on the GSP platform is
  equivalent to "alert1" threshold (`r alert1` `r info$units`) with the
  AutoDelfia.

\FloatBarrier

## Transfer of "conc5", "conc8", "alert2" and "alert3"

* "conc5" GA $\le$ 33.0 = 200
* "conc8" GW < 1000 = 160
* "alert2" BW 1000-2499 = 200
* "alert3" BW <1000 = 300

* The comparison data set was filtered to remove values <120 nmol/L

```{r, fig.cap="\\label{fig:dem58}Filtered Deming regression"}
conc58 <- comp %>%  ## comp is created in the comparison file
     filter(AD >= 120)  ## data close to the threshold

conc58.deming <- mcreg(x = conc58$AD, y =conc58$GSP, error.ratio = 1, alpha = 0.05,
                     mref.name = "AD", mtest.name = "GSP", sample.names = NULL,
                     method.reg = "Deming", method.ci = "bootstrap",
                     method.bootstrap.ci = "BCa",
                     nsamples = 999, rng.seed = NULL, rng.kind = "Mersenne-Twister", iter.max = 30,
                     threshold = 1e-06, na.rm = TRUE, NBins = 1e+06)

plot(conc58.deming, x.lab = "AD", y.lab = "GSP", main=paste(params$analyte, "Conc5 and Conc8 Thresholds Comparison"))
```

```{r}    
pander::pander(conc58.deming@para, caption = "\\label{tab:conc58}Regression Parameters")
```

```{r,fig.cap="\\label{fig:diff58}Difference Plot"}
plotDifference(conc58.deming, main= paste(params$analyte, "Threshold Comparision"))
```

```{r}
conc58intercept <- conc58.deming@para[1,1] # intercept
conc58slope <- conc58.deming@para[2,1] # slope
``` 
  
* The regression parameters (table \ref{tab:conc58}) were used to
  determine the effect of the GSP method on the Conc5 and Conc8 thresholds.

* A `r params$analyte` result of `r reg(conc58slope, conc5,
  conc58intercept)` `r info$units` on the GSP platform is
  equivalent to "conc5" threshold (`r conc5` `r info$units`) with the
  AutoDelfia.
  
* A `r params$analyte` result of `r reg(conc58slope, conc8,
  conc58intercept)` `r info$units` on the GSP platform is
  equivalent to "conc8" threshold (`r conc8` `r info$units`) with the
  AutoDelfia.

* A `r params$analyte` result of `r reg(conc58slope, alert2,
  conc58intercept)` `r info$units` on the GSP platform is
  equivalent to "alert2" threshold (`r alert2` `r info$units`) with the
  AutoDelfia.
  
  * A `r params$analyte` result of `r reg(conc58slope, alert3,
  conc58intercept)` `r info$units` on the GSP platform is equivalent
  to "alert3" threshold (`r alert2` `r info$units`) with the
  AutoDelfia. The vendor reported upper limit of the AMR for this
  assay is 300 nmol/L, despite a lack of AutoDelfia data flanking 300 nmol/L
  it is clear that the GSP has a slight negative bias in this
  concentration range.

## Screening Threshold Validation

```{r}



\FloatBarrier


