# Precision Study #

## Preliminary Precision ##

```{r}
prelim <- read_xls(params$file, sheet = sheets$prelim)

##### Functions for preliminary precision
### 20 repeats of QC material on the same day

prelim %>%
    gather(level, result, level1:level3) %>%
    group_by(instrument,level) %>%
    summarize(n = n(),
              mean = mean(result),
              sd = sd(result),
              cv = sd/mean *100) %>%
    pander::pander(caption = "\\label{tab:prelim}Preliminary Precision")
```

## Within and Between Run Precision ##

Five runs with three repetitions each were done to provide within-run
and between-run precision data. Analysis follows the calculations and
examples described in cite:Krouwer1984.  The data collection was
carried out at three levels, the results are presented in tables

Total imprecision was determined by pooling the variances of the
within and between day runs. Repeatability (aka: within-run precision)
was determined from within run replicates according to CLSI
guidelines. Total imprecision was compared against the manufacturer
claim.


```{r, fig.cap="\\label{fig:QC_den}Distribution of QC Results by Instrument"}
precision <- read_xls(params$file, sheet = sheets$precision)
precision %<>% na.omit()


# QC distribution
precision %>%
    gather(rep, result, rep1:rep3) %>%
    ggplot(aes(result, fill = factor(level))) +
    geom_density(alpha = 0.5) +
    facet_grid(instrument~.) +
    xlab(paste(params$analyte, info$units)) +
    scale_fill_discrete("Level")

``` 


```{r, fig.cap="\\label{fig:LJ} Levey-Jennings Charts"}
# Pseudo LJ charts
precision %>%
    gather(rep, result, rep1:rep3) %>%
    ggplot(aes(x = run, y = result, colour= factor(instrument))) +
    geom_point() +
    stat_summary(fun.y=mean, geom="line") +
    stat_summary(fun.data = mean_se, geom = "errorbar") +
    facet_grid(level~., scales = "free_y") +
    xlab("Run") +
    ylab(info$units) + 
    scale_colour_discrete("Instrument")

``` 


```{r}
## Within-run imprecision
within <- precision %>%
    gather(rep, result, rep1:rep3) %>%
    group_by(instrument, level, run) %>%
    summarize(n = n(),
              mean = mean(result),
              var = var(result)) %>%
    group_by(instrument, level) %>%
    summarize(n = sum(n),
              mean = mean(mean),
              var_within = mean(var))
              
## Between-run imprecision
between <- precision %>%
    gather(rep, result, rep1:rep3) %>%
    group_by(instrument, level, run) %>%
    summarize(n = n(),
              mean = mean(result)) %>%
    group_by(instrument, level) %>%
    summarize(n = sum(n),
              var_btwn = var(mean))
              

## Total imprecision
within$var_btwn <- between$var_btwn

within %>%
    group_by(instrument, level) %>%
    summarize(mean = mean,
              sd_within = sqrt(var_within),
              sd_btwn = sqrt(var_btwn),
              sd_total = sqrt(var_within + var_btwn),
              cv_total = sd_total/mean * 100) %>%
    pander::pander(caption = "\\label{tab:pre}Within and Between Run Precision by Instrument")

within %>%
    group_by(level) %>%
    summarize(mean= mean(mean),
              sd_within = (sqrt(mean(var_within))),
              sd_btwn = sqrt(mean(var_btwn)),
              sd_total = sqrt(mean(var_within + var_btwn)),
              cv_total = sd_total/mean * 100) %>%
    pander::pander(caption = "\\label{tab:ppre}Pooled Within and Between Run Precision")

```



\FloatBarrier
