# Screening Thresholds #

```{r}
reg <- function(m,x,b){
      y <- m * x + b
      return(round(y, digits = 3))
}

borderline <- 13
cutoff <- 17
alert <- 100
gates <- 50
```

* TSH screening employs a positive and borderline thresholds
    * positive $\ge$ 17
    * borderline $\ge$ 13
    * alert $\ge$ 100
    * gates $\ge$ 50

* Comparison data from samples near the screening thresholds was used to calculate regression equations

## Borderline Threshold ##

* The comparison data set was filtered to remove values less than 5 mIU/L and greater than 20 mIU/L.

```{r, fig.cap="\\label{fig:dem}Filtered Deming regression"}
bl <- comp %>%  ## comp is created in the comparison file
     filter(AD >= 5 & AD <= 20)  ## data close to the borderline threshold

bl.deming <- mcreg(x = bl$AD, y =bl$GSP, error.ratio = 1, alpha = 0.05,
                     mref.name = "AD", mtest.name = "GSP", sample.names = NULL,
                     method.reg = "Deming", method.ci = "bootstrap",
                     method.bootstrap.ci = "BCa",
                     nsamples = 999, rng.seed = NULL, rng.kind = "Mersenne-Twister", iter.max = 30,
                     threshold = 1e-06, na.rm = TRUE, NBins = 1e+06)

plot(bl.deming, x.lab = "AD", y.lab = "GSP", main=paste(params$analyte, "Borderline Threshold Comparison"))
```

```{r}    
pander::pander(bl.deming@para, caption = "\\label{tab:bl}Regression Parameters")
```

```{r,fig.cap="\\label{fig:diff}Difference Plot"}
plotDifference(bl.deming, main= paste(params$analyte, "Borderline Threshold Comparision"))
```

```{r}
blintercept <- bl.deming@para[1,1] # intercept
blslope <- bl.deming@para[2,1] # slope
``` 
  
* The regression parameters (table \ref{tab:bl}) were used to
  determine the effect of the GSP method on the borderline threshold.

* A `r params$analyte` result of `r reg(blslope, borderline,
  blintercept)` `r info$units` on the GSP platform is equivalent to
  borderline value (`r borderline` `r info$units`) with the AutoDelfia.
  
  
## Positive Threshold ##

* The comparison data set was filtered to remove values less than 7 mIU/L and greater than 27 mIU/L.

```{r, fig.cap="\\label{fig:dem}Filtered Deming regression"}
co <- comp %>%  ## comp is created in the comparison file
     filter(AD >= 7 & AD <= 27)  ## data close to the borderline threshold

co.deming <- mcreg(x = co$AD, y =co$GSP, error.ratio = 1, alpha = 0.05,
                     mref.name = "AD", mtest.name = "GSP", sample.names = NULL,
                     method.reg = "Deming", method.ci = "bootstrap",
                     method.bootstrap.ci = "BCa",
                     nsamples = 999, rng.seed = NULL, rng.kind = "Mersenne-Twister", iter.max = 30,
                     threshold = 1e-06, na.rm = TRUE, NBins = 1e+06)

plot(co.deming, x.lab = "AD", y.lab = "GSP", main=paste(params$analyte, "Positive Threshold Comparision"))
```

```{r}    
pander::pander(co.deming@para, caption = "\\label{tab:co}Regression Parameters")
```

```{r,fig.cap="\\label{fig:diff}Difference Plot"}
plotDifference(co.deming, main= paste(params$analyte, "Positive Threshold Comparision"))
```

```{r}
cointercept <- co.deming@para[1,1] # intercept
coslope <- co.deming@para[2,1] # slope
``` 
  
* The regression parameters (table \ref{tab:co}) were used to
  determine the effect of the GSP method on the screening threshold.

* A `r params$analyte` result of `r reg(coslope, cutoff, cointercept)`
  `r info$units` on the GSP platform is equivalent to a value at the
  screening threshold (`r cutoff` `r info$units`) with the AutoDelfia.
  
  
## Alert and Gates Thresholds ##

* The comparison data set was filtered to remove values less than 17 mIU/L.

```{r, fig.cap="\\label{fig:dem_al}Filtered Deming regression"}
al <- comp %>%  ## comp is created in the comparison file
     filter(AD > 13)  

al.deming <- mcreg(x = al$AD, y = al$GSP, error.ratio = 1, alpha = 0.05,
                     mref.name = "AD", mtest.name = "GSP", sample.names = NULL,
                     method.reg = "Deming", method.ci = "bootstrap",
                     method.bootstrap.ci = "BCa",
                     nsamples = 999, rng.seed = NULL, rng.kind = "Mersenne-Twister", iter.max = 30,
                     threshold = 1e-06, na.rm = TRUE, NBins = 1e+06)

plot(al.deming, x.lab = "AD", y.lab = "GSP", main=paste(params$analyte, "Alert Threshold Comparision"))
```

```{r}    
pander::pander(al.deming@para, caption = "\\label{tab:al}Regression Parameters")
```

```{r,fig.cap="\\label{fig:diff_alert}Difference Plot"}
plotDifference(co.deming, main= paste(params$analyte, "Positive Threshold Comparision"))
```

```{r}
alintercept <- al.deming@para[1,1] # intercept
alslope <- al.deming@para[2,1] # slope
``` 
  
* The regression parameters (table \ref{tab:al}) were used to
  determine the effect of the GSP method on the screening threshold.

* A `r params$analyte` result of `r reg(alslope, alert, alintercept)`
  `r info$units` on the GSP platform is equivalent to a value at the
  screening threshold (`r alert` `r info$units`) with the AutoDelfia.
  
  * A `r params$analyte` result of `r reg(alslope, gates, alintercept)`
  `r info$units` on the GSP platform is equivalent to a value at the
  screening threshold (`r gates` `r info$units`) with the AutoDelfia.

\FloatBarrier

